nmainla R package
===============

`nmainla` is an R package for Network Meta-Analysis using INLA.

Building
--------
The installation of R package 'INLA' is compulsory for successful usage. The 'INLA' package can be obtained from <http://www.r-inla.org>. We recommend the testing version, which can be downloaded by running:

```{r, echo=TRUE, eval=FALSE}
install.packages("INLA", repos = "https://www.math.ntnu.no/inla/R/testing")
```


Then, `nmainla` can be installed using `devtools` package as follows:

```{r, echo=TRUE, eval=FALSE}
library(devtools)
install_github("gunhanb/nmainla")
```


Testing
-------

The `testthat` package is used for testing. Tests reside in the
`tests/testthat` directory. 


License
-------

    nmainla is free software: you can redistribute it and/or modify
    it under the terms of the GNU General Public License as published by
    the Free Software Foundation, either version 3 of the License, or
    (at your option) any later version.

    nmainla is distributed in the hope that it will be useful,
    but WITHOUT ANY WARRANTY; without even the implied warranty of
    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
    GNU General Public License for more details.

    You should have received a copy of the GNU General Public License
    along with nmainla  If not, see <http://www.gnu.org/licenses/>.

